An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets

### 2021-11-18 ju-hofmann/ju-hofmann.Rmd
re-structure reproducible folder, completed

source("../code/func_collection.R")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "\\textwidth",
  fig.align = "center",
#  cache=TRUE,
  dpi = 100,
  warning = FALSE,
  message = FALSE
)
```

@@

In this paper we present an open-source implementation of the algorithm of the Congruent Matching Profile Segments (CMPS) method.
@cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its use in some examples of comparing bullet signature correlations.
Although @cmps conceptually describe the CMPS algorithm in their paper, the authors did not release an implementation of their method.
Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
Our implementation is made available as part of the `R` package \pkg{cmpsR} on GitHub at \url{https://github.com/willju-wangqian/cmpsR}.

@@

The thin white horizontal line in \autoref{fig:process}(a) indicates which cross-section was identified by the algorithm to represent the LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional view.
Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)).
A non-parametric LOESS smooth [@loess] is fitted to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth.
Note, that in @cmps bullet signatures are referred to as bullet profiles.
However, to avoid confusion, we distinguish the notion of bullet signatures from bullet profiles.
Bullet profiles are shown in panels (b), (c), and (d) of \autoref{fig:process}, while \autoref{fig:process}(f) shows the corresponding bullet signature.
Identifying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny], \pkg{bulletinspectR} to identify and correct those errors.
An example of the extraction process with corresponding code and parameter settings can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}. Note that the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.

```{r bullet, echo=FALSE, out.width=".8\\textwidth", fig.cap="Photo of a traditionally rifled gun barrel (left) and a fired bullet (right)."}
# knitr::include_graphics("img/barrel_bullet_ps.png", dpi = 100)
knitr::include_graphics("ju-hofmann_files/figure-latex/barrel_bullet_ps.png", dpi = 100)
```

```{r process, echo=FALSE, out.width=".9\\textwidth", fig.cap="A framework of obtaining a bullet signature. (a) rendering from the 3D topographic scan of a land engraved area (LEA). The selected crosscut location is indicated by a thin white horizontal line. (b) view of the cross-section of the land engraved area at the white line in (a). (c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves. (d) the crosscut data after chopping the left and right grooves. (e) the fitted curvature using LOESS. (f) after removing the curvature from the crosscut data, the bullet signature is obtained"}
knitr::include_graphics("ju-hofmann_files/figure-latex/figure1_v2.png", dpi = 100)
```

@@

Most algorithms for comparing striation marks are based on the digitized signatures and produce a similarity score [@song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940].
The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm.
The algorithm's main idea is to take a set of consecutive and non-overlapping basis segments from the comparison and for each segment find the "best" registration position on the reference (the other bullet signature) with respect to their cross-correlation values.
From a comparison of these registration positions, a **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
Note that researchers in @cmps refer to the origin of basis segments as the reference, but in this paper we refer to it as the comparison signature.
High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair.
Low scores between pairs of signatures are attributed to different source pairs.
However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not provided in @cmps, instead the threshold depends on the underlying structure of the data and the choice of parameters.   In a legal setting this variability is problematic because it allows for situations in which experts could choose parameters based on whether they are witnesses for the defense or the prosecution. 
Further research is needed to understand how to determine optimal threshold settings.
The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
<!--Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.-->
Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package \pkg{cmpsR} available from both CRAN and Github \url{https://github.com/willju-wangqian/cmpsR}. This publicly available implementation calculates the CMPS score of a comparison using the following code:

@@

<!-- ??? We shouldn't talk about the median version, should we? -->

<!-- \wj{Instead of computing the mean CMPS scores of matching and non-matching comparisons, a variation of $\mathrm{\overline{CMPS}_{diff}}$ is to compute the median CMPS scores of matching and non-matching comparisons. Computing the median could be beneficial if extreme values are observed for non-matching comparisons. More examples are provided in the Results section} -->

@@

```{r hamby252-data-seg, eval=TRUE, echo=FALSE}
# for hamby 252
N <- 8 # the number of different sets of parameters
CMPS_hamby252_results <- list() # a container for everything

#### setup span1
CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))

#### setup signature name
CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
  # list("sigs75", "sigs25", "sigs25_1062", "sigs15")

#### setup npeaks.set
CMPS_hamby252_results$npeaks.set <- lapply(1:N, function(t) c(5,3,1))

#### setup seg_length
CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200))

#### setup Tx
CMPS_hamby252_results$Tx <- as.list(rep(25, N))

#### setup outlength
CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)

#### create a plot title and a file name for each set of parameters
CMPS_hamby252_results$titlee <- list()
CMPS_hamby252_results$filename <- list()
for (i in 1:N) {
  CMPS_hamby252_results$titlee[[i]] <-
    paste0(
      "npeaks.set=c(",
      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
      ")",
      ", len=",
      CMPS_hamby252_results$seg_length[[i]],
      ", Tx=",
      CMPS_hamby252_results$Tx[[i]],
      ", \nspan1=",
      CMPS_hamby252_results$span1[[i]],
      ", span2=0.03"
    )
  CMPS_hamby252_results$filename[[i]] <- 
    paste(
      "hamby252_segment",
      CMPS_hamby252_results$span1[[i]]*100,
      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
      CMPS_hamby252_results$seg_length[[i]],
      CMPS_hamby252_results$Tx[[i]],
      sep = "_"
    )
}

#### container for the cmps results and corresponding plots
CMPS_hamby252_results$cmps.table <- list()
CMPS_hamby252_results$plot <- list()

#### a global title for Hamby252 plots
com.title252 <- expression(paste(
  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
))

for(i in 1:N){
  CMPS_hamby252_results$cmps.table[[i]] <- 
  read.csv(file = paste("./data/hamby252/", 
                        CMPS_hamby252_results$filename[[i]], 
                        ".csv",
                        sep = ""))
}

CMPS_hamby252_results_seg <- CMPS_hamby252_results

```{r hamby252-data-npeak, eval=TRUE, echo=FALSE}
N <- 8 # the number of different sets of parameters
CMPS_hamby252_results <- list() # a container for everything

#### setup span1
CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))

#### setup signature name
CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
# list("sigs75", "sigs25", "sigs25_1062", "sigs15")

#### setup npeaks.set
CMPS_hamby252_results$npeaks.set <- 
  list(c(5),
       c(5,2),
       c(5,3,1),
       c(10,6,2),
       c(6,4,2,1),
       c(10,7,4,2),
       c(10,6,4,2,1),
       c(10,8,6,4,2,1))

#### setup seg_length
CMPS_hamby252_results$seg_length <- 
  # as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
  as.list(rep(50, N))

#### setup Tx
CMPS_hamby252_results$Tx <- as.list(rep(25, N))

#### setup outlength
CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)
CMPS_hamby252_results$outlength[[7]] <- c(60, 90, 120, 150, 180)
CMPS_hamby252_results$outlength[[8]] <- c(50,75,100,125,150,200)

#### create a plot title and a file name for each set of parameters
CMPS_hamby252_results$titlee <- list()
CMPS_hamby252_results$filename <- list()
for (i in 1:N) {
  CMPS_hamby252_results$titlee[[i]] <-
    paste0(
      "npeaks.set=c(",
      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
      ")",
      ", len=",
      CMPS_hamby252_results$seg_length[[i]],
      ", Tx=",
      CMPS_hamby252_results$Tx[[i]],
      ", \nspan1=",
      CMPS_hamby252_results$span1[[i]],
      ", span2=0.03"
    )
  CMPS_hamby252_results$filename[[i]] <- 
    paste(
      "hamby252_npeak",
      CMPS_hamby252_results$span1[[i]]*100,
      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
      CMPS_hamby252_results$seg_length[[i]],
      CMPS_hamby252_results$Tx[[i]],
      sep = "_"
    )
}

#### container for the cmps results and corresponding plots
CMPS_hamby252_results$cmps.table <- list()
CMPS_hamby252_results$plot <- list()

#### a global title for Hamby252 plots
com.title252 <- expression(paste(
  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
))

for(i in 1:N){
  CMPS_hamby252_results$cmps.table[[i]] <- 
  read.csv(file = paste("./data/hamby252/", 
                        CMPS_hamby252_results$filename[[i]], 
                        ".csv",
                        sep = ""))
}

CMPS_hamby252_results_npeak <- CMPS_hamby252_results

```{r hamby44-data-seg, eval=TRUE, echo=FALSE}
N <- 8 # the number of different sets of parameters
CMPS_hamby44_results <- list() # a container for everything

#### setup span1
CMPS_hamby44_results$span1 <- as.list(rep(0.25, N))

#### setup signature name
CMPS_hamby44_results$signame <-
  as.list(rep("sigs25_531", N))

#### setup neapks.set
CMPS_hamby44_results$npeaks.set <-
  lapply(1:N, function(t) c(5,3,1))

#### setup seg_length
CMPS_hamby44_results$seg_length <- as.list(c(30, 45, 61, 90, 122, 150, 180, 210))

#### setup outlength
CMPS_hamby44_results$outlength <- vector(mode = "list", length = N)

#### setup Tx
CMPS_hamby44_results$Tx <- as.list(rep(30, N))

#### create a plot title and a file name for each set of parameters
CMPS_hamby44_results$titlee <- list()
CMPS_hamby44_results$filename <- list()
for (i in 1:N) {
  CMPS_hamby44_results$titlee[[i]] <-
    paste0(
      "npeaks.set=c(",
      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
      ")",
      ", len=",
      CMPS_hamby44_results$seg_length[[i]],
      ", Tx=",
      CMPS_hamby44_results$Tx[[i]],
      ", \nspan1=",
      CMPS_hamby44_results$span1[[i]],
      ", span2=0.03"
    )
  CMPS_hamby44_results$filename[[i]] <- 
    paste(
      "hamby44_segment",
      CMPS_hamby44_results$span1[[i]]*100,
      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
      CMPS_hamby44_results$seg_length[[i]],
      CMPS_hamby44_results$Tx[[i]],
      sep = "_"
    )
}

#### container for the cmps results and corresponding plots
CMPS_hamby44_results$cmps.table <- list()
CMPS_hamby44_results$plot <- list()

@@

for(i in 1:N){
  CMPS_hamby44_results$cmps.table[[i]] <- 
  read.csv(file = paste("./data/hamby44/", 
                        CMPS_hamby44_results$filename[[i]], 
                        ".csv",
                        sep = ""))
}

CMPS_hamby44_results_seg <- CMPS_hamby44_results

```{r hamby44-data-npeak, eval=TRUE, echo=FALSE}
N <- 8 # the number of different sets of parameters
CMPS_hamby44_results <- list() # a container for everything

#### setup span1
CMPS_hamby44_results$span1 <- as.list(rep(0.25, N))

#### setup signature name
CMPS_hamby44_results$signame <-
  as.list(rep("sigs25_531", N))

#### setup neapks.set
CMPS_hamby44_results$npeaks.set <-
  list(c(5),
       c(5,2),
       c(5,3,1),
       c(10,6,2),
       c(6,4,2,1),
       c(10,7,4,2),
       c(10,6,4,2,1),
       c(10,8,6,4,2,1))

#### setup seg_length
CMPS_hamby44_results$seg_length <- as.list(rep(61, N))

#### setup outlength
CMPS_hamby44_results$outlength <- vector(mode = "list", length = N)
CMPS_hamby44_results$outlength[[7]] <- c(61, 91, 121, 151, 181)
CMPS_hamby44_results$outlength[[8]] <- c(61, 91, 121, 151, 181, 211)

#### setup Tx
CMPS_hamby44_results$Tx <- as.list(rep(30, N))

#### create a plot title and a file name for each set of parameters
CMPS_hamby44_results$titlee <- list()
CMPS_hamby44_results$filename <- list()
for (i in 1:N) {
  CMPS_hamby44_results$titlee[[i]] <-
    paste0(
      "npeaks.set=c(",
      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
      ")",
      ", len=",
      CMPS_hamby44_results$seg_length[[i]],
      ", Tx=",
      CMPS_hamby44_results$Tx[[i]],
      ", \nspan1=",
      CMPS_hamby44_results$span1[[i]],
      ", span2=0.03"
    )
  CMPS_hamby44_results$filename[[i]] <- 
    paste(
      "hamby44_npeak",
      CMPS_hamby44_results$span1[[i]]*100,
      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
      CMPS_hamby44_results$seg_length[[i]],
      CMPS_hamby44_results$Tx[[i]],
      sep = "_"
    )
}

#### container for the cmps results and corresponding plots
CMPS_hamby44_results$cmps.table <- list()
CMPS_hamby44_results$plot <- list()

for(i in 1:N){
  CMPS_hamby44_results$cmps.table[[i]] <- 
  read.csv(file = paste("./data/hamby44/", 
                        CMPS_hamby44_results$filename[[i]], 
                        ".csv",
                        sep = ""))
}

CMPS_hamby44_results_npeak <- CMPS_hamby44_results
```

```{r rf-data-load, echo=FALSE}
rf.results <- list()
rf.results[[1]] <- read.csv(file = "./data/hamby252/hamby252_rf_results.csv")
rf.results[[2]] <- read.csv(file = "./data/hamby44/hamby44_rf_results.csv")

rf.tt <- lapply(rf.results, function(rf_result) {
  with(rf_result, {
    tibble(rf.diff, rf.max, rf.maxbar) %>% 
      apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
  })
}) %>% do.call(rbind, .) %>% as_tibble()

>>>>

# source("../code/func_collection.R")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "\\textwidth",
  fig.align = "center",
#  cache=TRUE,
  dpi = 144,
  warning = FALSE,
  message = FALSE
)
```

@@

In this paper we present an open-source implementation of the algorithm of the Congruent Matching Profile Segments (CMPS) method.
@cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its use in some examples of comparing bullet signature correlations.
Although @cmps conceptually describe the CMPS algorithm in their paper, the authors did not release an implementation of their method.
Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
<!-- Our implementation is made available as part of the `R` package \pkg{cmpsR} on GitHub at \url{https://github.com/willju-wangqian/cmpsR}. -->
\wj{change}
Our implementation is made available as part of the `R` package \pkg{cmpsR} on CRAN.

@@

The thin white horizontal line in \autoref{fig:process}(a) indicates which cross-section was identified by the algorithm to represent the LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional view.
Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)).
A non-parametric LOESS smooth [@loess] is fitted to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth.
Note, that in @cmps bullet signatures are referred to as bullet profiles.
However, to avoid confusion, we distinguish the notion of bullet signatures from bullet profiles.
Bullet profiles are shown in panels (b), (c), and (d) of \autoref{fig:process}, while \autoref{fig:process}(f) shows the corresponding bullet signature.
Identifying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny], \pkg{bulletinspectR} to identify and correct those errors.
An example of the extraction process with corresponding code and parameter settings can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}. Note that the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.
\wj{can be found in the supplementary materials of this paper? }

```{r bullet, echo=FALSE, out.width=".8\\textwidth", fig.cap="Photo of a traditionally rifled gun barrel (left) and a fired bullet (right)."}
# knitr::include_graphics("img/barrel_bullet_ps.png", dpi = 100)
knitr::include_graphics("ju-hofmann_files/figure-latex/barrel_bullet_ps.png", dpi = 144)
```

```{r process, echo=FALSE, out.width=".9\\textwidth", fig.cap="A framework of obtaining a bullet signature. (a) rendering from the 3D topographic scan of a land engraved area (LEA). The selected crosscut location is indicated by a thin white horizontal line. (b) view of the cross-section of the land engraved area at the white line in (a). (c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves. (d) the crosscut data after chopping the left and right grooves. (e) the fitted curvature using LOESS. (f) after removing the curvature from the crosscut data, the bullet signature is obtained"}
knitr::include_graphics("ju-hofmann_files/figure-latex/figure1_v2.png", dpi = 144)
```

@@

Most algorithms for comparing striation marks are based on the digitized signatures and produce a similarity score [@song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940].
The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm.
The algorithm's main idea is to take a set of consecutive and non-overlapping basis segments from the comparison and for each segment find the "best" registration position on the reference (the other bullet signature) with respect to their cross-correlation values.
From a comparison of these registration positions, a **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
Note that researchers in @cmps refer to the origin of basis segments as the reference, but in this paper we refer to it as the comparison signature.
High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair.
Low scores between pairs of signatures are attributed to different source pairs.
However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not provided in @cmps, instead the threshold depends on the underlying structure of the data and the choice of parameters.   In a legal setting this variability is problematic because it allows for situations in which experts could choose parameters based on whether they are witnesses for the defense or the prosecution. 
Further research is needed to understand how to determine optimal threshold settings.
The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package \pkg{cmpsR} available from both CRAN and Github \url{https://github.com/willju-wangqian/cmpsR}. This publicly available implementation calculates the CMPS score of a comparison using the following code:
\wj{ignore github?}

@@

@@

```{r load-results, eval=TRUE, echo=FALSE}
all_results_container <- readRDS("data/CMPSpaper_results.rds")

CMPS_hamby252_results_seg <- all_results_container$h252_seg
CMPS_hamby252_results_npeak <- all_results_container$h252_npeak
CMPS_hamby44_results_seg <- all_results_container$h44_seg
CMPS_hamby44_results_npeak <- all_results_container$h44_npeak
rf.results <- all_results_container$rf

@@

#### a global title for Hamby252 plots
com.title252 <- expression(paste(
  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
))
```

<!-- ```{r hamby252-data-seg, eval=TRUE, echo=FALSE} -->
<!-- # for hamby 252 -->
<!-- N <- 8 # the number of different sets of parameters -->
<!-- CMPS_hamby252_results <- list() # a container for everything -->

<!-- #### setup span1 -->
<!-- CMPS_hamby252_results$span1 <- as.list(rep(0.25, N)) -->

<!-- #### setup signature name -->
<!-- CMPS_hamby252_results$signame <- as.list(rep("sigs25", N)) -->
<!--   # list("sigs75", "sigs25", "sigs25_1062", "sigs15") -->

<!-- #### setup npeaks.set -->
<!-- CMPS_hamby252_results$npeaks.set <- lapply(1:N, function(t) c(5,3,1)) -->

<!-- #### setup seg_length -->
<!-- CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200)) -->

<!-- #### setup Tx -->
<!-- CMPS_hamby252_results$Tx <- as.list(rep(25, N)) -->

<!-- #### setup outlength -->
<!-- CMPS_hamby252_results$outlength <- vector(mode = "list", length = N) -->

<!-- #### create a plot title and a file name for each set of parameters -->
<!-- CMPS_hamby252_results$titlee <- list() -->
<!-- CMPS_hamby252_results$filename <- list() -->
<!-- for (i in 1:N) { -->
<!--   CMPS_hamby252_results$titlee[[i]] <- -->
<!--     paste0( -->
<!--       "npeaks.set=c(", -->
<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","), -->
<!--       ")", -->
<!--       ", len=", -->
<!--       CMPS_hamby252_results$seg_length[[i]], -->
<!--       ", Tx=", -->
<!--       CMPS_hamby252_results$Tx[[i]], -->
<!--       ", \nspan1=", -->
<!--       CMPS_hamby252_results$span1[[i]], -->
<!--       ", span2=0.03" -->
<!--     ) -->
<!--   CMPS_hamby252_results$filename[[i]] <-  -->
<!--     paste( -->
<!--       "hamby252_segment", -->
<!--       CMPS_hamby252_results$span1[[i]]*100, -->
<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"), -->
<!--       CMPS_hamby252_results$seg_length[[i]], -->
<!--       CMPS_hamby252_results$Tx[[i]], -->
<!--       sep = "_" -->
<!--     ) -->
<!-- } -->

<!-- #### container for the cmps results and corresponding plots -->
<!-- CMPS_hamby252_results$cmps.table <- list() -->
<!-- CMPS_hamby252_results$plot <- list() -->

<!-- #### a global title for Hamby252 plots -->
<!-- com.title252 <- expression(paste( -->
<!--   "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
<!-- )) -->

<!-- for(i in 1:N){ -->
<!--   CMPS_hamby252_results$cmps.table[[i]] <-  -->
<!--   read.csv(file = paste("./data/hamby252/",  -->
<!--                         CMPS_hamby252_results$filename[[i]],  -->
<!--                         ".csv", -->
<!--                         sep = "")) -->
<!-- } -->

<!-- CMPS_hamby252_results_seg <- CMPS_hamby252_results -->

<!-- ```{r hamby252-data-npeak, eval=TRUE, echo=FALSE} -->
<!-- N <- 8 # the number of different sets of parameters -->
<!-- CMPS_hamby252_results <- list() # a container for everything -->

<!-- #### setup span1 -->
<!-- CMPS_hamby252_results$span1 <- as.list(rep(0.25, N)) -->

<!-- #### setup signature name -->
<!-- CMPS_hamby252_results$signame <- as.list(rep("sigs25", N)) -->
<!-- # list("sigs75", "sigs25", "sigs25_1062", "sigs15") -->

<!-- #### setup npeaks.set -->
<!-- CMPS_hamby252_results$npeaks.set <-  -->
<!--   list(c(5), -->
<!--        c(5,2), -->
<!--        c(5,3,1), -->
<!--        c(10,6,2), -->
<!--        c(6,4,2,1), -->
<!--        c(10,7,4,2), -->
<!--        c(10,6,4,2,1), -->
<!--        c(10,8,6,4,2,1)) -->

<!-- #### setup seg_length -->
<!-- CMPS_hamby252_results$seg_length <-  -->
<!--   # as.list(c(25, 50, 75, 100, 125, 150, 175, 200)) -->
<!--   as.list(rep(50, N)) -->

<!-- #### setup Tx -->
<!-- CMPS_hamby252_results$Tx <- as.list(rep(25, N)) -->

<!-- #### setup outlength -->
<!-- CMPS_hamby252_results$outlength <- vector(mode = "list", length = N) -->
<!-- CMPS_hamby252_results$outlength[[7]] <- c(60, 90, 120, 150, 180) -->
<!-- CMPS_hamby252_results$outlength[[8]] <- c(50,75,100,125,150,200) -->

<!-- #### create a plot title and a file name for each set of parameters -->
<!-- CMPS_hamby252_results$titlee <- list() -->
<!-- CMPS_hamby252_results$filename <- list() -->
<!-- for (i in 1:N) { -->
<!--   CMPS_hamby252_results$titlee[[i]] <- -->
<!--     paste0( -->
<!--       "npeaks.set=c(", -->
<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","), -->
<!--       ")", -->
<!--       ", len=", -->
<!--       CMPS_hamby252_results$seg_length[[i]], -->
<!--       ", Tx=", -->
<!--       CMPS_hamby252_results$Tx[[i]], -->
<!--       ", \nspan1=", -->
<!--       CMPS_hamby252_results$span1[[i]], -->
<!--       ", span2=0.03" -->
<!--     ) -->
<!--   CMPS_hamby252_results$filename[[i]] <-  -->
<!--     paste( -->
<!--       "hamby252_npeak", -->
<!--       CMPS_hamby252_results$span1[[i]]*100, -->
<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"), -->
<!--       CMPS_hamby252_results$seg_length[[i]], -->
<!--       CMPS_hamby252_results$Tx[[i]], -->
<!--       sep = "_" -->
<!--     ) -->
<!-- } -->

<!-- #### container for the cmps results and corresponding plots -->
<!-- CMPS_hamby252_results$cmps.table <- list() -->
<!-- CMPS_hamby252_results$plot <- list() -->

<!-- #### a global title for Hamby252 plots -->
<!-- com.title252 <- expression(paste( -->
<!--   "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
<!-- )) -->

<!-- for(i in 1:N){ -->
<!--   CMPS_hamby252_results$cmps.table[[i]] <-  -->
<!--   read.csv(file = paste("./data/hamby252/",  -->
<!--                         CMPS_hamby252_results$filename[[i]],  -->
<!--                         ".csv", -->
<!--                         sep = "")) -->
<!-- } -->

<!-- CMPS_hamby252_results_npeak <- CMPS_hamby252_results -->

<!-- ```{r hamby44-data-seg, eval=TRUE, echo=FALSE} -->
<!-- N <- 8 # the number of different sets of parameters -->
<!-- CMPS_hamby44_results <- list() # a container for everything -->

<!-- #### setup span1 -->
<!-- CMPS_hamby44_results$span1 <- as.list(rep(0.25, N)) -->

<!-- #### setup signature name -->
<!-- CMPS_hamby44_results$signame <- -->
<!--   as.list(rep("sigs25_531", N)) -->

<!-- #### setup neapks.set -->
<!-- CMPS_hamby44_results$npeaks.set <- -->
<!--   lapply(1:N, function(t) c(5,3,1)) -->

<!-- #### setup seg_length -->
<!-- CMPS_hamby44_results$seg_length <- as.list(c(30, 45, 61, 90, 122, 150, 180, 210)) -->

<!-- #### setup outlength -->
<!-- CMPS_hamby44_results$outlength <- vector(mode = "list", length = N) -->

<!-- #### setup Tx -->
<!-- CMPS_hamby44_results$Tx <- as.list(rep(30, N)) -->

<!-- #### create a plot title and a file name for each set of parameters -->
<!-- CMPS_hamby44_results$titlee <- list() -->
<!-- CMPS_hamby44_results$filename <- list() -->
<!-- for (i in 1:N) { -->
<!--   CMPS_hamby44_results$titlee[[i]] <- -->
<!--     paste0( -->
<!--       "npeaks.set=c(", -->
<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","), -->
<!--       ")", -->
<!--       ", len=", -->
<!--       CMPS_hamby44_results$seg_length[[i]], -->
<!--       ", Tx=", -->
<!--       CMPS_hamby44_results$Tx[[i]], -->
<!--       ", \nspan1=", -->
<!--       CMPS_hamby44_results$span1[[i]], -->
<!--       ", span2=0.03" -->
<!--     ) -->
<!--   CMPS_hamby44_results$filename[[i]] <-  -->
<!--     paste( -->
<!--       "hamby44_segment", -->
<!--       CMPS_hamby44_results$span1[[i]]*100, -->
<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"), -->
<!--       CMPS_hamby44_results$seg_length[[i]], -->
<!--       CMPS_hamby44_results$Tx[[i]], -->
<!--       sep = "_" -->
<!--     ) -->
<!-- } -->

<!-- #### container for the cmps results and corresponding plots -->
<!-- CMPS_hamby44_results$cmps.table <- list() -->
<!-- CMPS_hamby44_results$plot <- list() -->

<!-- #### a global title for Hamby44 plots -->
<!-- com.title44 <- expression(paste( -->
<!--   "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
<!-- )) -->

<!-- for(i in 1:N){ -->
<!--   CMPS_hamby44_results$cmps.table[[i]] <-  -->
<!--   read.csv(file = paste("./data/hamby44/",  -->
<!--                         CMPS_hamby44_results$filename[[i]],  -->
<!--                         ".csv", -->
<!--                         sep = "")) -->
<!-- } -->

<!-- CMPS_hamby44_results_seg <- CMPS_hamby44_results -->

<!-- ```{r hamby44-data-npeak, eval=TRUE, echo=FALSE} -->
<!-- N <- 8 # the number of different sets of parameters -->
<!-- CMPS_hamby44_results <- list() # a container for everything -->

<!-- #### setup span1 -->
<!-- CMPS_hamby44_results$span1 <- as.list(rep(0.25, N)) -->

<!-- #### setup signature name -->
<!-- CMPS_hamby44_results$signame <- -->
<!--   as.list(rep("sigs25_531", N)) -->

<!-- #### setup neapks.set -->
<!-- CMPS_hamby44_results$npeaks.set <- -->
<!--   list(c(5), -->
<!--        c(5,2), -->
<!--        c(5,3,1), -->
<!--        c(10,6,2), -->
<!--        c(6,4,2,1), -->
<!--        c(10,7,4,2), -->
<!--        c(10,6,4,2,1), -->
<!--        c(10,8,6,4,2,1)) -->

<!-- #### setup seg_length -->
<!-- CMPS_hamby44_results$seg_length <- as.list(rep(61, N)) -->

<!-- #### setup outlength -->
<!-- CMPS_hamby44_results$outlength <- vector(mode = "list", length = N) -->
<!-- CMPS_hamby44_results$outlength[[7]] <- c(61, 91, 121, 151, 181) -->
<!-- CMPS_hamby44_results$outlength[[8]] <- c(61, 91, 121, 151, 181, 211) -->

<!-- #### setup Tx -->
<!-- CMPS_hamby44_results$Tx <- as.list(rep(30, N)) -->

<!-- #### create a plot title and a file name for each set of parameters -->
<!-- CMPS_hamby44_results$titlee <- list() -->
<!-- CMPS_hamby44_results$filename <- list() -->
<!-- for (i in 1:N) { -->
<!--   CMPS_hamby44_results$titlee[[i]] <- -->
<!--     paste0( -->
<!--       "npeaks.set=c(", -->
<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","), -->
<!--       ")", -->
<!--       ", len=", -->
<!--       CMPS_hamby44_results$seg_length[[i]], -->
<!--       ", Tx=", -->
<!--       CMPS_hamby44_results$Tx[[i]], -->
<!--       ", \nspan1=", -->
<!--       CMPS_hamby44_results$span1[[i]], -->
<!--       ", span2=0.03" -->
<!--     ) -->
<!--   CMPS_hamby44_results$filename[[i]] <-  -->
<!--     paste( -->
<!--       "hamby44_npeak", -->
<!--       CMPS_hamby44_results$span1[[i]]*100, -->
<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"), -->
<!--       CMPS_hamby44_results$seg_length[[i]], -->
<!--       CMPS_hamby44_results$Tx[[i]], -->
<!--       sep = "_" -->
<!--     ) -->
<!-- } -->

<!-- #### container for the cmps results and corresponding plots -->
<!-- CMPS_hamby44_results$cmps.table <- list() -->
<!-- CMPS_hamby44_results$plot <- list() -->

<!-- #### a global title for Hamby44 plots -->
<!-- com.title44 <- expression(paste( -->
<!--   "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
<!-- )) -->

<!-- for(i in 1:N){ -->
<!--   CMPS_hamby44_results$cmps.table[[i]] <-  -->
<!--   read.csv(file = paste("./data/hamby44/",  -->
<!--                         CMPS_hamby44_results$filename[[i]],  -->
<!--                         ".csv", -->
<!--                         sep = "")) -->
<!-- } -->

<!-- CMPS_hamby44_results_npeak <- CMPS_hamby44_results -->
